---
title: MPDX Analysis
output: html_document
params:
  timeint: month
  effthreshpct: 1
  effthreshweek: 26
---

```{r preamble, echo=F, message=F, warning = F, error = F}
suppressMessages(library(dplyr))
back_env <- new.env()
back_env$param_efficiency_analysis_threshold_pct <- params$effthreshpct
back_env$param_efficiency_analysis_threshold_week <- params$effthreshweek
back_env$param_time_interval <- params$timeint
back_env$param_user_set_result_directory_name <- params$usersetcsvdir
back_env$param_sess_dur_data_query_name <- params$sessqueryname
sys.source("./src/presentation_backend.r", envir = back_env)
```
# MPDx Fundraising Analysis

## Summary of Results

The three MPDX cohorts that used the platform had more success in their
fundraising, on average, than the cohorts that didn't use the platform.

However, the cause of this success is unclear. There is insufficient evidence
to suggest that it can be attributed to:

*  Platform activity
*  Actions in spaces (a proxy for Champion energy on platform)
*  Content progress on platform
*  Assessment Responses

## Goal drop-off 
If a fundraiser goes too long without meeting their support goal, they become
increasingly unlikely to ever meet it. Cohorts who used Gloo were much more
likely to reach their fundraising goal than the pre-Gloo cohorts.


### Probability of attaining fundraising goal, Gloo users.

The underlying data for this graph can be found in
line\_probability\_drop\_off.csv

```{r, echo=F, message=F, warning = F, fig.width = 8, fig.height = 6}
cutoff_week <- 14
pct_reached_after_cutoff <- backend.user_success_pct %>%
  filter(
    days_since_class == cutoff_week * 7
  , gloo_cohort
  , variable == "pct_will_succeed"
  ) %>% {
    .$value
  }
pct_ever_reached_from_gloo <- back_env$pct_ever_reached %>%
  filter(gloo_cohort) %>% {
    .$pct_will_succeed
  }
```
Among Gloo users, `r round(100 * pct_ever_reached_from_gloo, 1)` % 
of users ever reached their fundraising
goal. But among users who hadn't reached their goal by week `r cutoff_week`,
only `r round(100 * pct_reached_after_cutoff, 1)` % will ever reach their goal.

```{r, echo=F, message=F, warning = F, fig.width = 8, fig.height = 6}
plotly::ggplotly(back_env$user_success_plot_gloo)
```

### Probability of attaining fundraising goal, all users.

The underlying data for this graph can be found in
line\_probability\_drop\_off\_pre\_gloo.csv

```{r, echo=F, message=F, warning = F, fig.width = 8, fig.height = 6}
cutoff_week <- 14
pct_reached_after_cutoff <- backend.user_success_pct %>%
  filter(
    days_since_class == cutoff_week * 7
  , !gloo_cohort
  , variable == "pct_will_succeed"
  ) %>% {
    .$value
  }
pct_ever_reached_non_gloo <- back_env$pct_ever_reached %>%
  filter(!gloo_cohort) %>% {
    .$pct_will_succeed
  }
```
Among all users, `r round(100 * pct_ever_reached_non_gloo, 1)` % of 
users ever reached their fundraising
goal. But among users who hadn't reached their goal by week `r cutoff_week`,
only `r round(100 * pct_reached_after_cutoff, 1)` % will ever reach their goal.

```{r, echo=F, message=F, warning = F, fig.width = 8, fig.height = 6}
plotly::ggplotly(back_env$user_success_plot_non_gloo)
```

## Performance Distributions

### Funds Raised Per Week

The underlying data for this graph can be found in
bar\_chart\_funds\_per\_week.csv

```{r, echo=F, message=F, fig.width = 8, fig.height = 6}
avg_funds_raised_per_week_nongloo <- back_env$funds_raised_per_week_summary_stats %>%
  filter(!post_gloo) %>% {
    .$avg_funds_raised_per_week
  }
avg_funds_raised_per_week_gloo <- back_env$funds_raised_per_week_summary_stats %>%
  filter(post_gloo) %>% {
    .$avg_funds_raised_per_week
  }
diff_avg_funds = avg_funds_raised_per_week_gloo -
  avg_funds_raised_per_week_nongloo
```

Gloo users raised an average of \$`r round(avg_funds_raised_per_week_gloo, 2)`
per week, whereas non-Gloo users raised an average of
\$`r round(avg_funds_raised_per_week_nongloo, 2)`. Gloo users raised
\$`r round(diff_avg_funds, 2)` per week more than non-Gloo users on average.

```{r, echo=F, message=F, fig.width = 8, fig.height = 6}
back_env$funds_raised_vs_on_platform_all
```

### Percentage of Goal Attained

The underlying data for this graph can be found in
bar\_chart\_pct\_goal\_attained.csv

```{r, echo=F, message=F, fig.width = 8, fig.height = 6}
max_pct_summary_stats <- presentation_functions.get_max_pct_summary_stats(
  back_env$funds_vs_pas_all
, back_env$param_efficiency_analysis_threshold_pct
)
pct_reached_nongloo <- max_pct_summary_stats %>%
  filter(post_gloo == "Before Gloo") %>% {
    .$pct_reached_threshold
  }
pct_reached_gloo <- max_pct_summary_stats %>%
  filter(post_gloo == "After Gloo") %>% {
    .$pct_reached_threshold
  }
```

`r round(100 * pct_reached_gloo, 1)` % of Gloo users 
raised at least 
`r round(100 * back_env$param_efficiency_analysis_threshold_pct, 1)` % of their goal. In contrast, 
`r round(100 * pct_reached_nongloo, 1)` % of non-Gloo users
raised at least `r round(100 * back_env$param_efficiency_analysis_threshold_pct, 1)` % of their goal.

```{r, echo=F, message=F, fig.width = 8, fig.height = 6}
back_env$max_pct_vs_on_platform_all
```

### Efficiency Analysis

The underlying data for this chart can be found in
bar\_chart\_efficiency\_analysis.csv

`r round(100 * back_env$pct_gloo_users_past_timeframe, 1)`% of Gloo users took more than
`r back_env$param_efficiency_analysis_threshold_week - 1` weeks to reach 
`r round(100 * back_env$param_efficiency_analysis_threshold_pct, 1)`% 
of their support goal. 
Among Gloo users who reached the `r round(100 * back_env$param_efficiency_analysis_threshold_pct, 1)`%
threshold in `r back_env$param_efficiency_analysis_threshold_week - 1` weeks or less, the average time to reach 
the threshold was approximately 
`r round(back_env$avg_time_to_thresh_gloo, 1)` weeks.

`r round(100 * back_env$pct_other_users_past_timeframe, 1)`% of non-Gloo users took more than
`r back_env$param_efficiency_analysis_threshold_week - 1` weeks to reach 
`r round(100 * back_env$param_efficiency_analysis_threshold_pct, 1)`% 
of their support goal.
Among non-Gloo users who reached the `r round(100 * back_env$param_efficiency_analysis_threshold_pct, 1)`%
threshold in `r back_env$param_efficiency_analysis_threshold_week - 1` weeks or less, the average time 
to reach threshold was approximately 
`r round(back_env$avg_time_to_thresh_other, 1)` weeks.


```{r, echo=F, message=F, fig.width = 8, fig.height = 6}
back_env$plot_time_to_threshold
```

## Platform activity unrelated to fundraising success
### Total Platform Actions

The underlying data for this chart can be found in
scatter\_max\_pct\_vs\_pas.csv

```{r, echo=F, message=F, fig.width = 8, fig.height = 6}
plotly::ggplotly(
  back_env$plot_max_pct_vs_pas +
    ggplot2::scale_y_continuous(labels = percent)
)
summary(back_env$lm_max_pct_vs_pas)
```

### Space Activity

The underlying data for this chart can be found in
scatter\_max\_pct\_vs\_spaces.csv

```{r, echo=F, message=F, fig.width = 8, fig.height = 6}
plotly::ggplotly(
  back_env$plot_max_pct_vs_spaces +
    ggplot2::scale_y_continuous(labels = percent)
)
summary(back_env$lm_max_pct_vs_spaces)
```

### Content Progress

The underlying data for this chart can be found in
scatter\_max\_pct\_vs\_content_progress.csv

```{r, echo=F, message=F, fig.width = 8, fig.height = 6}
plotly::ggplotly(
  back_env$plot_max_pct_vs_content_progress +
    ggplot2::scale_y_continuous(labels = percent)
)
summary(back_env$lm_max_pct_vs_content_progress)
```

## Fundraising amount (relative to goal) is not correlated to assessment responses

### Hand

The underlying data for this chart can be found in
scatter\_pct\_goal\_vs\_hand.csv

```{r, echo=F, message=F, warning = F, fig.width = 8, fig.height = 6}
back_env$plot_pct_goal_vs_hand_no_zeros +
  ggplot2::scale_y_continuous(labels = percent)
summary(back_env$lm_pct_goal_vs_hand_no_zeros)
```

### Heart

The underlying data for this chart can be found in
scatter\_pct\_goal\_vs\_heart.csv

```{r, echo=F, message=F, warning = F, fig.width = 8, fig.height = 6}
back_env$plot_pct_goal_vs_heart_no_zeros +
  ggplot2::scale_y_continuous(labels = percent)
summary(back_env$lm_pct_goal_vs_heart_no_zeros)
```

### Head

The underlying data for this chart can be found in
scatter\_pct\_goal\_vs\_head.csv

```{r, echo=F, message=F, warning = F, fig.width = 8, fig.height = 6}
back_env$plot_pct_goal_vs_head_no_zeros +
  ggplot2::scale_y_continuous(labels = percent)
summary(back_env$lm_pct_goal_vs_head_no_zeros)
```

## Assessment Volatility Through Time

The underlying data for this chart can be found in
scatter\_volatility.csv and trend\_volatility.csv

Volatility is calculated as the standard deviation of assessment responses
within each given week.

```{r, echo=F, message=F, warning = F, fig.width = 8, fig.height = 6}
plotly::ggplotly(back_env$plot_h3_vol)
```

## Retention Curve

The underlying data for this chart can be found in
retention_curve_data.csv

```{r, echo=F, message=F, warning = F, fig.width = 8, fig.height = 6}
plotly::ggplotly(back_env$plot_retention_curve)
```
